On the link between functional traits and growth rate: meta-analysis shows effects change with plant size, as predicted

### 2016-03-01 MS.tex
Add Lizzy comments on the new version of the results and the mat & met

The dataset included studies differing in the growth measurement used (relative or absolute), the number of species, the experimental conditions (stressed vs unstressed), and the concordance between stages used to measure trait and growth rate. However, these differences are clear criteria for assessing the quality of the data for addressing our hypotheses. Consequently, we adopted a three-stage approach where at first we were conservative by focusing exclusively on relative growth rate, across studies that included \underline{\textgreater} 10 species, under unstressed conditions, and where the source of the trait and growth is the same (expect for maximum height and seed mass, where a particular stage is by definition required to measure the trait). We then compared these results with those focusing on relative growth rate from the entire dataset - with all criteria relaxed excepted the growth measurement used. Finally, we compared results from both relative and absolute growth rates from the entire dataset.

@@

Results from the entire dataset reinforced our conclusions for both SLA and wood density, and did not altered them for the others traits. For SLA and wood density, although the number of replicates doubled by using the entire dataset, effect sizes and overall results were similar to those reported above using the conservative crieteria (Fig. \ref{fig:fig3})). For seed mass and Aarea, the additional replicates in the entire dataset allowed us to be more confident of the effect size for seedling stage (Fig \ref{fig:fig3}d, e). Comparison of Aarea effect between the conservative and relaxed criteria (Fig. \ref{fig:fig3}d), indicated little effect of stress (here mainly low light) on the correlation with relative growth rate at seedling stage as the correlation was still positive when 8 correlations measured under low light conditions were added. For maximum height, there were no additional replicates in the entire dataset; we still cannot conclude undoubtedly that the correlation is absent for smaller sizes.

@@

We had hypothesized only for seed mass that the correlation between trait and growth rate would change if absolute growth rate was used instead of relative growth rate. Overall, the models fit did not improve when growth measurement was incorporated (see log likelihood ratio tests in Fig. \ref{fig:fig4}). For a majority of traits, effect sizes were generally consistent between relative growth rate and absolute growth rate when both measurements were available (e.g. effect size for relative and absolute growth rate of Hmax and Wood density at adult stage in Fig. \ref{fig:fig4} b and c). However, for seed mass and wood density at seedling stage, the direction of effect sizes changed when correlations were measured with either abolute or relative growth rate. For seed mass, effect size at seedling stage with relative growth rate was positive and shifted to non significant with absolute growth rate (Fig \ref{fig:fig4}d; CI overlapping zero). While these results were consistent with expectations, our ability to conclude was limited due to low sample size for correlation with absolute growth rate (i.e CIs overlapping, Fig. \ref{fig:fig4}d). For wood density, some differences occurred according to the growth measurement used, but they were not easily attributed to any single cause. In particular, the correlation at juvenile stage shifted from negative with relative growth rate to non significant with absolute growth rate (i.e CI included zero, Fig. \ref{fig:fig4}b). Yet, the correlation coefficients recorded for absolute growth rate came from \citet{Augspurger:1984ct}, and unlike others they used wood density values from adult plants together with growth from juveniles. So it was not possible to disentangle the effect of growth measurement from the effect of trait origin.

@@

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig3.pdf}
\caption{The relationship between relative growth rates (RGR) and traits changes with ontogenetic stage and trait. Plots show the effect size (+ 95\% confidence intervals; CI) for the average correlation by ontogenetic stage. Effect size is a standardized measure of the deviation of correlation coefficient from zero (Fisher's z-transformed). Effects are significant if CIs for a given stage do not overlap with zero. Trait names as in Fig. \ref{fig:fig1}. $n$ indicates number of correlations contributing to each effect. Results shown are for the "conservative dataset" (i.e. correlations that included \underline{\textgreater} 10 species, under unstressed conditions, and where the source of the trait and growth is the same) and for the entire dataset (i.e. with all criteria relaxed, see methods for details). Likelihood Ratio Tests (LRT) compared maximum-likelihood fits between a pooled model and one separated by stage for the conservative dataset. A significant p-value means adding a stage effect to the model significantly improved model fit.}
\label{fig:fig3}
\end{figure}

>>>>

The dataset included studies differing in the growth measurement used (relative or absolute), the number of species, the experimental conditions (stressed vs unstressed), and the concordance between stages used to measure trait and growth rate. These differences provide good criteria for assessing the quality of the data for addressing our hypotheses. We adopted a three-stage approach where at first we were conservative by focusing exclusively on relative growth rate, across studies that included \underline{\textgreater} 10 species, under unstressed conditions, and where the trait and growth were measured at the same stage (expect for maximum height and seed mass, where a particular stage is by definition required to measure the trait). We then compared these results with those from the subset of the dataset using relative growth rate, but with all other criteria relaxed. Finally, we compared results from both relative and absolute growth rates from the entire dataset.

@@

Results from the entire dataset reinforced our conclusions for both SLA and wood density, and did not alter them for the others traits. For SLA and wood density, although the number of replicates doubled by using the entire dataset, effect sizes and overall results were similar to those reported above using the conservative crieteria (Fig. \ref{fig:fig3})). For seed mass and Aarea, the additional replicates in the entire dataset allowed us to be more confident of the effect size for seedling stage (Fig \ref{fig:fig3}d, e). Comparison of Aarea effect between the conservative and relaxed criteria (Fig. \ref{fig:fig3}d), indicated little effect of stress (here mainly low light) on the correlation with relative growth rate at seedling stage as the correlation was still positive when 8 correlations measured under low light conditions were added. For maximum height, there were no additional replicates in the entire dataset; we still cannot conclude undoubtedly that the correlation is absent for smaller sizes.

@@

The only correlation that we hypothesized would change if absolute growth rate was used instead of relative growth rate, was for eed mass. Overall, the models fit did not improve when growth measurement was incorporated (see log likelihood ratio tests in Fig. \ref{fig:fig4}). For a majority of traits, effect sizes were generally consistent between relative growth rate and absolute growth rate when both measurements were available (e.g. effect size for relative and absolute growth rate of Hmax and Wood density at adult stage in Fig. \ref{fig:fig4} b and c). However, for seed mass and wood density at seedling stage, the direction of effect sizes changed when correlations were measured with abolute versus relative growth rate. For seed mass, effect size at seedling stage with relative growth rate was positive and shifted to non significant with absolute growth rate (Fig \ref{fig:fig4}d; CI overlapping zero). While these results were consistent with expectations, our ability to conclude was limited due to low sample size for correlation with absolute growth rate (i.e CIs overlapping, Fig. \ref{fig:fig4}d). For wood density, some differences occurred according to the growth measurement used, but they were not easily attributed to any single cause. In particular, the correlation at juvenile stage shifted from negative with relative growth rate to non significant with absolute growth rate (i.e CI included zero, Fig. \ref{fig:fig4}b). Yet, the correlation coefficients recorded for absolute growth rate came from \citet{Augspurger:1984ct}, and unlike others they used wood density values from adult plants together with growth from juveniles. So it was not possible to disentangle the effect of growth measurement from the effect of trait origin.

@@

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig3.pdf}
\caption{The relationship between relative growth rates (RGR) and traits changes with ontogenetic stage and trait. Plots show the effect size (+ 95\% confidence intervals; CI) for the average correlation by ontogenetic stage. Effect size is a standardized measure of the deviation of correlation coefficient from zero (Fisher's z-transformed). Effects are significant if CIs for a given stage do not overlap with zero. Trait names as in Fig. \ref{fig:fig1}. $n$ indicates number of correlations contributing to each effect. Results shown are for the "conservative dataset" (i.e. correlations that included \underline{\textgreater} 10 species, under unstressed conditions, and where the trait and growth were measured at the same stage) and for the entire dataset (i.e. with all criteria relaxed, see methods for details). Likelihood Ratio Tests (LRT) compared maximum-likelihood fits between a pooled model and one separated by stage for the conservative dataset. A significant p-value means adding a stage effect to the model significantly improved model fit.}
\label{fig:fig3}
\end{figure}
